Untitled

### 2024-04-25 draft1.Rmd
Update draft1.Rmd
Tweaks

Foster’s objective is to understand what effects the changes in stiffness and damping in a piece of foam under repeated light compressions. The goal of our analysis is to discover patterns and build models to provide this understanding. With this understanding, the U.S. Military could improve the foam padding in marine special combat helmets, ideally so they can survive at least 10 years of regular use.

@@

|    Variable Name    |                   Description                                  |:--------------------|:---------------------------------------------------------------------------------------------|
        ID            |  the unique identifier of the different foam pieces
     chemIndex        |  the chemical makeup type of the foam. 1 = 79, 2 = 100, 3 = 121
      porosity        |  the porosity level of the foam. Low = 71%, high = 81%
       freq           |  the number of compressions per second (hz)
        amp           |  the amplitude of the compressions
    initialStrain     |  the initial measure of the strain of foam. (Originally labeled “strain”)
    initialStress     |  the initial measure of the stress of the foam. (Originally labeled “stresskpa”)
       cycle          |  the cycle number the measurement was taken at

@@

|    Variable Name    |                   Description                                        |:--------------------|:---------------------------------------------------------------------------------------------|
     stiffness        |  measurement of the foam’s stiffness. (Originally labeled “E1_MPA”)
      damping         |  measurement of the foam’s damping. (Originally labeled “delta_rad”)
    stiffnessFrac     |  $$\frac{\text{stiffness}}{\text{first stiffness measurement}}$$
     dampingFrac      |  $$\frac{\text{tan(damping)}}{\text{tan(first damping measurement)}}$$

@@

foam_data_scaled$intervalCode == "N"

>>>>

Foster’s objective is to understand what affects the changes in stiffness and damping in a piece of foam under repeated light compressions. The goal of our analysis is to discover patterns and build models to provide this understanding. With this understanding, the U.S. Military could improve the foam padding in marine special combat helmets, ideally so they can survive at least 10 years of regular use.

@@

|    Variable Name    |                   Description                                 |
|:--------------------|:---------------------------------------------------------------------------------------------|
|        ID            |  the unique identifier of the different foam pieces|
|     chemIndex        |  the chemical makeup type of the foam. 1 = 79, 2 = 100, 3 = 121|
|      porosity        |  the porosity level of the foam. Low = 71%, high = 81%|
|       freq           |  the number of compressions per second (hz)|
|        amp           |  the amplitude of the compressions|
|    initialStrain     |  the initial measure of the strain of foam. (Originally labeled “strain”)|
|    initialStress     |  the initial measure of the stress of the foam. (Originally labeled “stresskpa”)|
|       cycle          |  the cycle number the measurement was taken at|

@@

|    Variable Name    |                   Description                                       |
|:--------------------|:---------------------------------------------------------------------------------------------|
|     stiffness        |  measurement of the foam’s stiffness. (Originally labeled “E1_MPA”)|
|      damping         |  measurement of the foam’s damping. (Originally labeled “delta_rad”)|
|    stiffnessFrac     |  stiffness / first stiffness measurement|
|     dampingFrac      |  tan(damping) / tan(first damping measurement)

@@

#foam_data_scaled$intervalCode == "N"
